NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-04-20 Manuscript/manuscriptPS.tex
Update Figs. 6 and 10, and update caption for Fig. 5.
Figs. 6 and 10 are formatted in the style of NMRlipids II (with scripts to make the new figures included in the Figs/scripts).

In Fig 5 caption, the M and F are now formatted just like in NMRlipids I. Alternate formatting could be {\textbf{\footnotesize F}} which makes the font bold and a tiny bit smaller.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
    Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}.
    Here ÒMÓ indicates a magnitude problem, ÒFÓ a forking problem; letter size increases with problem severity. Color scheme: Òwithin experimental errorÓ (dark green), Òalmost within experimental errorÓ (light green), Òclear deviation from experimentsÓ (light red), and Òmajor deviation from experimentsÓ (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/NAdensPOPS.eps}
  \caption{\label{NAdensPOPS}
    Counterion density profiles along the membrane normal and areas per lipid (A$_{\rm pl}$)
    of POPS lipid bilayer from simulations with different force fields.
    The experimental area per lipid is~62.7~$\pm$~1.3~\AA$^2$~\cite{pan14}.
  }
  \todo{Commented by M. Javanainen in blog:
    MacRog pure POPS is simulated with Verlet cutoff scheme, Piggot is rerunning with group cutoff scheme. Check if affects results \& update figures when ready} \\
  \todo{It has been suggested that we should format this with the same style as in NMRlipids II: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/44}
\end{figure}

@@

\subsection{Ca$^{2+}$ binding affinity to bilayers with negatively charged PS lipids}
\begin{figure}[tb]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixtureLOWcons.eps}
  \caption{\label{CAdensPCPSmixture}
    Number density profiles of Ca$^{2+}$ from POPC:POPS (5:1) mixtures simulated with different force fields.
    The smallest simulated CaCl$_2$ concentrations are shown.
    The density profiles for all the simulated concentrations are given in SI figure \ref{CAdensPCPSmixtureALL}.
  }
  \todo{Should we include also counterions into the plot?} \\
  \todo{It has been suggested that we should format this with the same style as in NMRlipids II: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/44}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
    Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}.
    Here {\textsf{\small M}} indicates a magnitude problem, {\textsf{\small F}} a forking problem; letter size increases with problem severity. Color scheme: "within experimental error" (dark green), "almost within experimental error" (light green), "clear deviation from experiments" (light red), and "major deviation from experiments" (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/NAdensPOPSformatted.pdf}
  \caption{\label{NAdensPOPS}
    Counterion density profiles along the membrane normal and areas per lipid (A$_{\rm pl}$)
    of POPS lipid bilayer from simulations with different force fields.
    The experimental area per lipid is~62.7~$\pm$~1.3~\AA$^2$~\cite{pan14}.
  }
  \todo{Commented by M. Javanainen in blog:
    MacRog pure POPS is simulated with Verlet cutoff scheme, Piggot is rerunning with group cutoff scheme. Check if affects results \& update figures when ready} \\
  \todo{It has been suggested that we should format this with the same style as in NMRlipids II: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/44}
\end{figure}

@@

\subsection{Ca$^{2+}$ binding affinity to bilayers with negatively charged PS lipids}
\begin{figure}[tb]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixtureLOWconsformatted.pdf}
  \caption{\label{CAdensPCPSmixture}
    Number density profiles of Ca$^{2+}$ from POPC:POPS (5:1) mixtures simulated with different force fields.
    The smallest simulated CaCl$_2$ concentrations are shown.
    The density profiles for all the simulated concentrations are given in SI figure \ref{CAdensPCPSmixtureALL}.
  }
  \todo{Should we include also counterions into the plot?} \\
  \todo{It has been suggested that we should format this with the same style as in NMRlipids II: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/44}
\end{figure}
